---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## externalrdata

[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip) [![Travis-CI Build Status](https://travis-ci.org/jsta/externalrdata.svg?branch=master)](https://travis-ci.org/jsta/externalrdata) [![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/externalrdata)](https://cran.r-project.org/package=externalrdata) [![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/externalrdata)](https://cran.r-project.org/package=externalrdata)

This package is a template R package to fetch, cache, and serve data from external sources. All data sources are assumed to be `csv` files. The typical workflow would be to fork this package and rename the project-specific pieces including:
 
 * `temp_get`
    * _baseurl_
    * _files_
 * `cache_path`
    * _appname_
    * _appauthor_
 * function prefixes (e.g. change `temp_get` to `myspecificproject_get`)

## Installation

```{r eval=FALSE}
# install devtools if not found
# install.packages(devtools)
devtools::install_github("jsta/externalrdata")
```

## Usage

```{r }
library(externalrdata)
```

### Download external data and store in file system

```{r }
# these files have metadata headers that need to be skipped
temp_get("1", skip = c(16, 38))
```

### Load data

```{r }
lapply(temp_load("1"), head)
```
